Fig1

### 2020-04-17 analysis/figure-1.Rmd
now all of fig2 script in fig 1 script

```{r}
#write.csv(chartsne, "../../musicalgenes/data/tsne.csv")
```

>>>>

# supple table 1 of all but control-bldg DEGs

```{r}
suppletable1 <- allDEG %>%
  filter(comparison != "control_bldg") %>%
  group_by(sex, tissue, comparison) %>%
  arrange( tissue, sex, direction, gene)
head(suppletable1)

write_csv(suppletable1, "../results/suppletable1.csv")

# save file for musical genes https://raynamharris.shinyapps.io/musicalgenes/
#write.csv(allDEG, "../../musicalgenes/data/allDEG.csv")

# tsne files too big to save
#write.csv(chartsne, "../../musicalgenes/data/tsne.csv")
```
